---
title: "STA 141A Data Integration (Keep)"
author: "Judah Hsu"
date: "2023-06-08"
output: html_document
---
## Section 3: Data Integration

### Clustering

In order to perform the data integration, I'll first look at clusters
and then PCA. In particular, in order to integrate the "spks" value for
each trial, I've decided to add a column for significant brain areas and
for each column, I'll add the average number of spikes for that brain
area in a given trial. I've chosen average vs. aggregate or proportion
because both the proportion of "spks" and its aggregate are dependent on
the amount of neurons recorded for that brain area.

From there, I'll cluster the points for every possible pair of brain
areas, highlight the trials by color (success/failure), and see which
metric seems to cluster the trials most accurately. Additionally, I'll
be trying different metrics as well as clustering methods.

First, however, there are 62 unique brain areas. Instead of adding 62
unique brain areas, I went through each session and found the proportion
of spikes each brain area accounts for. Then, I'll first remove brain
areas that appear in only one or two sessions since any trial without
that brain area recorded will have "NA" in it's place, making it hard to
cluster based on that brain area. Next, I'll take only the brain areas
that appear in 6+ sessions so that I'll be able to use said-brain areas
as metrics that work for a variety of trials. By this method, I'm left
with 7 brain areas that appear in 6+ sessions (CA1, CA3, DG, LGd, MOs,
VISp, and root)

```{r}
#CODE TO DETERMINE SIGNIFICANT BRAIN AREAS---------------------------------------------------------------------

#Find all brain areas
brains.all <- c()
for(i in 1:18){
  brains.all<-c(brains.all, session[[i]]$brain_area)
}
brains.unique <- brains.all %>% unique()

spks.total <- 0
#get total number of spikes in session 1
for (s in 1:length(session[[1]]$spks)){
  spks.total <- spks.total +sum(session[[1]]$spks[[s]])
}

#Get total number of spikes for each brain area in session 1, across neurons and trials
session1.unique <- session[[1]]$brain_area %>% unique()
session1.brain.props <- c()
for(i in 1:length(session1.unique)) {
  #Go through each brain area in session 1
  temp.total <- 0
  for(j in 1:length(session[[1]]$spks)){
    #Now for each brain area, go through each trial
    for(k in 1:length(session[[1]]$spks[[j]][,1])){
     #Now go through each neuron in trial and add the sum of the spks vector if the neuron brain area is equal to current brain raea
      #Then add that to the temp total
      if(session[[1]]$brain_area[j] == session1.unique[i]){
        temp.total <- temp.total + sum(session[[1]]$spks[[j]][k,])
      }
    }
  }
  session1.brain.props <- c(session1.brain.props, temp.total/spks.total)
  #now that you have temp total, add it to the proportion vector
}
df.brain.utility <- data.frame("brain areas" = session1.unique, props = session1.brain.props, "session number" = rep(1, length(session1.unique)))

for(s in 2:length(session)){
  session.unique <- session[[s]]$brain_area %>% unique()
  session.brain.props <- c()
  for(i in 1:length(session.unique)){
    temp.total <- 0
    for(j in 1:length(session[[s]]$spks)){
      for(k in 1:length(session[[s]]$spks[[j]][,1])){
        if(session[[s]]$brain_area[j] == session.unique[i]){
          temp.total <- temp.total + sum(session[[s]]$spks[[j]][k,])
        }
      }
    }
    session.brain.props <- c(session.brain.props, temp.total/spks.total)
  }
  #add info to df.brain.utility in the form of a row
  for(p in 1:length(session.brain.props)){
    df.brain.utility <- df.brain.utility %>% rbind(c(session.unique[p], session.brain.props[p], s))
  }
}

df.brain.utility <- df.brain.utility %>% arrange(brain.areas)
#Brain areas to take out: (* means it has 2 recordings)
#ACB, AUD, BLA, EPd, *GPe, ILA, LHm *LP, LS, LSc, MD, MEA, MG, MOp, MS, NB, OLF, ORB*, ORBm, OT, PAG, PIR, PO, POL, PT, RN, RSP, RT, SCs*, SCsg, SI, SNr, SPF, SSs, TT*, VISpm, VISrl, VPM*

#The ones that have a lot (6+ about a third of the sessions record them) are: #it's okay if props =0 bc that means SMTH was recorded
  #CA1 (2,3,4,5,6,8,9,10,12,13,14)
  #CA3 (1,7,8,9,15,16,18)
  #DG (1, 3, 4, 5, 8, 10, 12, 13)
  #LGd (4, 12, 13, 15, 16, 18)
  #MOs (1, 4, 5, 8, 12, 13, 14)
  #VISp (1, 3, 4, 8, 10, 12, 14)
  #root (1, 2, 3, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 15, 17, 18)
#CODE TO DETERMINE SIGNIFICANT BRAIN AREAS---------------------------------------------------------------------
#For clustering based on average brain areas
```







#Initializing df

```{r}
#Code to create new dataset, including spikes
library(tidyverse)
#Get session
session=list()
for(i in 1:18){
  session[[i]]=readRDS(paste(("/Users/judahhsu/Desktop/classes/STA 141A/sessions/session"),i,'.rds',sep=''))
  #print(session[[i]]$mouse_name)
  #print(session[[i]]$date_exp)
}

session1=cbind(session[[1]]$contrast_left,session[[1]]$contrast_right,rep(1,length(session[[1]]$contrast_left)),session[[1]]$mouse_name,length(session[[1]]$brain_area),length(unique(session[[1]]$brain_area)),length(session[[1]]$spks),session[[1]]$feedback_type)

session2=cbind(session[[2]]$contrast_left,session[[2]]$contrast_right,rep(2,length(session[[2]]$contrast_left)),session[[2]]$mouse_name,length(session[[2]]$brain_area),length(unique(session[[2]]$brain_area)),length(session[[2]]$spks),session[[2]]$feedback_type)

#make dataframe for rest of sessions
df <- (rbind(session1, session2))
for(i in 3:18){
  session.temp = cbind(session[[i]]$contrast_left,session[[i]]$contrast_right,rep(i,length(session[[i]]$contrast_left)),session[[i]]$mouse_name,length(session[[i]]$brain_area),length(unique(session[[i]]$brain_area)),length(session[[i]]$spks),session[[i]]$feedback_type)
  df <- rbind(df, session.temp)
}

#REMAKE DF
colnames(df) = c("contrast_left","contrast_right", "session","mouse","number_of_neurons","brain_area","number_of_trials", "feedback_type")
df = as.data.frame(df)
df$contrast_left = as.factor(df$contrast_left)
df$contrast_right = as.factor(df$contrast_right)
df$session = as.factor (df$session)
df$mouse = as.factor(df$mouse)
df$feedback_type = as.factor(df$feedback_type)

###ADD COLUMNS for each brain area -> Again, for average spikes per brain area
brain_column_prop <- function(area){
  props.temp <- c() 
  for(s in 1:length(session)){
    if(area %in% session[[s]]$brain_area){
      #If there's an actual record of CA1 in it
      for(tr in 1:length(session[[s]]$spks)){#For each trial
        #get total spikes in trial
        trial.spks <- sum(session[[s]]$spks[[tr]])
        brain.spks <- 0
        for(n in 1:length(session[[s]]$spks[[tr]][,1])){ #For every neuron
          if(session[[s]]$brain_area[[n]] == area){
            brain.spks <- brain.spks + sum(session[[s]]$spks[[tr]][n,])
          }
        }
        props.temp <- c(props.temp, brain.spks/trial.spks)
      }
    }
    else {
      #Otherwise, you just add NA for as many neuronsxtrials
      props.temp <- c(props.temp, rep(NA, length(session[[s]]$spks)))
    }
  }
  return(props.temp)
}

brain_column_ave <- function(area){
  aves.temp <- c() 
  for(s in 1:length(session)){
    if(area %in% session[[s]]$brain_area){
      #If there's an actual record of CA1 in it
      for(tr in 1:length(session[[s]]$spks)){#For each trial
        #get total spikes in trial
        brain.total <- sum(session[[s]]$brain_area == area) #instead find the number of neurons #that have that brain area
        brain.spks <- 0
        for(n in 1:length(session[[s]]$spks[[tr]][,1])){ #For every neuron
          if(session[[s]]$brain_area[[n]] == area){
            brain.spks <- brain.spks + sum(session[[s]]$spks[[tr]][n,])
          }
        }
        aves.temp <- c(aves.temp, brain.spks/brain.total)
      }
    }
    else {
      #Otherwise, you just add NA for as many neuronsxtrials
      aves.temp <- c(aves.temp, rep(NA, length(session[[s]]$spks)))
    }
  }
  return(aves.temp)
}


brain.add <- c('CA1', 'CA3', 'DG', 'LGd', 'MOs', 'VISp', 'root') #brain areas to be added as columns
add_props <- function(data){
  data <- cbind(data, 'CA1' = brain_column_prop("CA1"))
  data <- cbind(data, 'CA3' = brain_column_prop("CA3"))
  data <- cbind(data, 'DG' = brain_column_prop("DG"))
  data <- cbind(data, 'LGd' = brain_column_prop("LGd"))
  data <- cbind(data, 'MOs' = brain_column_prop("MOs"))
  data <- cbind(data, 'VISp' = brain_column_prop("VISp"))
  data <- cbind(data, 'root' = brain_column_prop("root")) 
  return(data)
}

add_aves <- function(data) {
  data <- cbind(data, 'CA1' = brain_column_ave("CA1"))
  data <- cbind(data, 'CA3' = brain_column_ave("CA3"))
  data <- cbind(data, 'DG' = brain_column_ave("DG"))
  data <- cbind(data, 'LGd' = brain_column_ave("LGd"))
  data <- cbind(data, 'MOs' = brain_column_ave("MOs"))
  data <- cbind(data, 'VISp' = brain_column_ave("VISp"))
  data <- cbind(data, 'root' = brain_column_ave("root")) 
  return(data)
}

#df <- add_aves(df)
```

#Plot based on average brain area across pairwise brain areas, color coded by feedback
```{r}

library(GGally)
#ggpairs(df[,9:ncol(df)], mapping = ggplot2::aes(colour = df$feedback_type, alpha=0.1))
####PLOT ONLY WORKS WITH THE AVERAGE BRAIN AREAS
```



#Code to add pc1 for top 5 neurons
```{r}
#Code to get top five neurons and their brain areas, and to do pca on them... should i do pca stratified by session? nah I don't think so and my reasoning is just because the more i split it up by sessions and stuff, the more complicated it gets

df.neuron <- matrix(ncol=10)
df.neuron <- data.frame(df.neuron)
names(df.neuron) <- c('neuron1', 'neuron2', 'neuron3', 'neuron4', 'neuron5', 'ba1', 'ba2', 'ba3', 'ba4', 'ba5')

#for every trial, create 5 columns of the first-5 spikes and brain areas... then PCA for the spikes and add the brain areas to the df
for (s in 1:length(session)){
  for(t in 1:length(session[[s]]$feedback_type)){
    tempSums <- session[[s]]$spks[[t]] %>% rowSums()
    order <- tempSums %>% order(decreasing=TRUE)
    temp.ba <- session[[s]]$brain_area[order]
    row.add <- c(tempSums[order][1:5], temp.ba[1:5])
    df.neuron <- rbind(df.neuron, row.add)
  } 
}

df.neuron <- na.omit(df.neuron)
df.neuron$neuron1 <- df.neuron$neuron1 %>% as.numeric()
df.neuron$neuron2 <- df.neuron$neuron2 %>% as.numeric()
df.neuron$neuron3 <- df.neuron$neuron3 %>% as.numeric()
df.neuron$neuron4 <- df.neuron$neuron4 %>% as.numeric()
df.neuron$neuron5 <- df.neuron$neuron5 %>% as.numeric()

pca.neuron <- prcomp(x=df.neuron[1:5], scale=TRUE)
plot(pca.neuron, type = "l", main = "Scree Plot")
pc1<-pca.neuron$rotation[,1] %>% matrix(nrow=5, ncol=1)
df.neuron <- cbind(df.neuron, pc1 = as.matrix(df.neuron[1:5]) %*% pc1)
df.neuron <- df.neuron[-1:-5]

df <- cbind(df, df.neuron) #Tis because i only did it for one session

#Turn all important categorical variables into factors or change them
df$ba1 <- as.factor(df$ba1)
df$ba2 <- as.factor(df$ba2)
df$ba3 <- as.factor(df$ba3)
df$ba4 <- as.factor(df$ba4)
df$ba5 <- as.factor(df$ba5)

#ggsave("fig_3.1.png",dpi = 300)
```




#Clustering
#Hot one encoding for session, brain area, contrast, pc1 & kmeans prediction
```{r}
library(caret)

#Encoded cat variales only
df.cat <- df %>% select(ba1:ba5, session)
encoded <- dummyVars("~.", data=df.cat) %>% predict(newdata=df.cat) #Fudge it created 302 variables..... oh 
  
#New dataset with original + encoded categorical variables
df.new <- cbind(df, encoded)

#One concern is how to label, do you arbitrarily label them? And I think yes. Because the purpose of this clustering is not to  predict the data itself but firstly to see the relation
 
kMeansMisclass <- function(selectdf){
  kmeans.cluster <- selectdf %>% kmeans(centers=2)

  #CONFUSION MATRIX
  cluster.names <- c("-1", "1")
  df.new$cluster <- cluster.names[kmeans.cluster$cluster] #GLOBAL VARIABLE

  #comparison <- table(df.new$feedback_type, df.new$cluster) #GLOBAL VARIABLE
  #print(comparison)

  #ALTERNATE CONFUSION MATRIX
  df.new$cluster <- as.factor(df.new$cluster) #GLOBAL VARIABLE

  # Create a confusion matrix
  confusion_matrix <- confusionMatrix(data = df.new$cluster, reference = df.new$feedback_type)


  #print(confusion_matrix)
  rate.class <- confusion_matrix$overall["Accuracy"]
  return(rate.class)
}

df.new %>% head()

#Get the average rate over many times
avg.class.rate <- function(selectdf){
  avg.accuracy <- c()
  for(i in 1:50){
    accuracy <- kMeansMisclass(selectdf)
    vals <- c(accuracy, 1-accuracy)
    avg.accuracy <- c(avg.accuracy, min(vals)) #So I'm printing the lower values. now I need to add and average them
  }
  return(sum(avg.accuracy)/50)
}

#One hot encoding for contrast, session, brain area, PC1
check <- df.new %>% select(contrast_left, contrast_right, pc1:session.9)
print(avg.class.rate(check)) #0.453454/0.546546

#One hot encoding for contrast, session, brain area... X PC1
check <- df.new %>% select(contrast_left, contrast_right, ba1.ACA:session.9)
print(avg.class.rate(check)) #0.3607006/0.6392994, assuming 2 clusters are dif by nature

#One hot encoding for contrast,, brain area, PC1... X Session
check <- df.new %>% select(contrast_left, contrast_right, pc1:ba5.ZI)
print(avg.class.rate(check)) #0.453454/0.546546 Taking out session literally does nothing...?

#One hot encoding for contrast, brain area... X PC1, Session So it does seem like PC1 and session don't make a difference
check <- df.new %>% dplyr::select(contrast_left, contrast_right, ba1.ACA:ba5.ZI)
print(avg.class.rate(check)) #0.3704428/0.546546

#One hot encoding for contrast, PC1, session X Brain area
check <- df.new %>% dplyr::select(contrast_left, contrast_right, pc1, session.1:session.9)
print(avg.class.rate(check)) #0.453454/0.546546

#One hot encoding for brain area
check <- df.new %>% dplyr::select(ba1.ACA:ba5.ZI)
print(avg.class.rate(check)) #0.3589569/0.6410431

#One hot encoding for contrast
check <- df.new %>% dplyr::select(contrast_left, contrast_right)
print(avg.class.rate(check)) #0.4376028/0.5623972

#One hot encoding for pc1
check <- df.new %>% dplyr::select(pc1)
print(avg.class.rate(check)) #0.453454/0.546546

#One hot encoding for session
check <- df.new %>% dplyr::select(session.1:session.9)
print(avg.class.rate(check)) #0.3142728/0.6857272

#One hot encoding for session & brain area
check <- df.new %>% dplyr::select(ba1.ACA:session.9)
print(avg.class.rate(check)) #0.3489431/0.6510569



#It appears as though brain area and session # are the best
```